---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "50%"
)
```

# visualize

<!-- badges: start -->
[![Travis-CI Build Status](https://travis-ci.org/coatless/visualize.svg?branch=master)](https://travis-ci.org/coatless/visualize)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/visualize)](http://www.r-pkg.org/pkg/visualize)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/visualize)](https://cran.r-project.org/package=visualize)
<!-- badges: end -->

The goal of visualize is to graph the pdf or pmf and highlight what area or
probability is present in user defined locations. Visualize is able to provide
lower tail, bounded, upper tail, and two tail calculations. Supports strict and
equal to inequalities. Also provided on the graph is the mean and variance of
the distribution.

## Installation

You can install the released version of visualize from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("visualize")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("coatless/visualize")
```

## Examples

To use visualize, load the package with:

```{r}
library("visualize")
```

Then, construct a graph by following the `visualize.dist()` pattern. For example,
the normal distribution can be shown with: 

```{r visualize-normal}
# Graph a standard normal distribution with a z-score of 1.96
visualize.norm(1.96)

# Change the location of the tail
visualize.norm(1.96, section = "upper")

# Shift the mean and create a bounded range.
visualize.norm(c(-1.96, 1.96), section = "bounded")
```

The parameters of the distribution can also be modified. Take for example the
Binomial distribution.

```{r visualize-binomial}
visualize.binom(stat = 9, size = 20, p = 0.5)

visualize.binom(stat = 9, size = 24, p = 0.25)
```

Discrete distributions can also handle a level of strict (`<`, `>`) or equal
to (`<=`, `>=`) inequality.


```{r discrete-inequalities}
visualize.pois(stat = c(4, 6), lambda = 3.5, section = "bounded",
  strict = c(TRUE, TRUE))

visualize.pois(stat = c(4, 6), lambda = 3.5, section = "bounded",
  strict = c(TRUE, FALSE))

visualize.pois(stat = c(4, 6), lambda = 3.5, section = "bounded",
  strict = c(FALSE, FALSE))
```


## Author

James Joseph Balamuta

## Citing the `visualize` package

To ensure future development of the package, please cite `visualize`
package if used during an analysis or simulation study. Citation information
for the package may be acquired by using in *R*:

```{r, eval = FALSE}
citation("visualize")
```

## License

MIT License
